Easy as Pi: A Network Coding Raspberry Pi Testbed

### 2016-06-05 testbed.tex
more testbed

@@

WRITE SOMETHING ABOUT THIS AND MENTION HOW TO REQUEST A KODO LICENSE

\item Build executables:
\begin{lstlisting}[]
$ python waf build
\end{lstlisting}
\FloatBarrier
\vspace{-5mm}

\item Navigate to the repository and configure \texttt{waf} by typing:
\texttt{python config.py} and select the 16th ``make specification'' file
for the \ac{Raspi}, e.g. option \texttt{[16]cxx\_raspberry\_gxx49\_arm}
presented by the file.

This command configures \texttt{waf} to use the proper compiler and its
required flags to generate the binaries for the \ac{Raspi}. If the
configuration was correct, the output will indicate:
\texttt{'configure' finished successfully (X.XXXs)}, where \texttt{X.XXX}
is total time in seconds for configuring the project in the server. \\

\item Execute \texttt{python waf build}. If the build process was
successful, the generated binaries for the \ac{Raspi} should be located
in \texttt{build/cxx\_raspberry\_gxx49\_arm} in the Kodo repository.
\textbf{Indicate how the binary files should look like}.

Once this procedure is made, the testbed administrator can relocate the
generated binary files to the \ac{Raspi}s through the network as desired
by using the \texttt{scp} command during the configuration step.

>>>>

WRITE SOME SMALL INTRO AND MENTION HOW TO REQUEST A KODO LICENSE

\item Build executables:
\begin{lstlisting}[]
$ python waf build
...
'build' finished successfully (2m22.918s)
\end{lstlisting}
\FloatBarrier
\vspace{-5mm}

\item SHARED and/or STATIC libraries
\item COPY TO RASPI
\item RUN EXECUTABLE encode\_decode\_simple

%\item Navigate to the repository and configure \texttt{waf} by typing:
%\texttt{python config.py} and select the 16th ``make specification'' file
%for the \ac{Raspi}, e.g. option \texttt{[16]cxx\_raspberry\_gxx49\_arm}
%presented by the file.
%
%This command configures \texttt{waf} to use the proper compiler and its
%required flags to generate the binaries for the \ac{Raspi}. If the
%configuration was correct, the output will indicate:
%\texttt{'configure' finished successfully (X.XXXs)}, where \texttt{X.XXX}
%is total time in seconds for configuring the project in the server. \\
%
%\item Execute \texttt{python waf build}. If the build process was
%successful, the generated binaries for the \ac{Raspi} should be located
%in \texttt{build/cxx\_raspberry\_gxx49\_arm} in the Kodo repository.
%\textbf{Indicate how the binary files should look like}.
%
%Once this procedure is made, the testbed administrator can relocate the
%generated binary files to the \ac{Raspi}s through the network as desired
%by using the \texttt{scp} command during the configuration step.

@@

WRITE HOW TO RUN A KODO PYTHON SCRIPT IN THE RASPIS

SHORT INTRO. EXPLAIN A FEW USECASES FOR FABRIC. E.G. REBOOT, INSTALL PACKAGE, RUN SCRIPT ON MULTIPLE RASPIS. COPY FILES TO/FROM PC AND MULTIPLE RASPIS
